We Are All Trying to Describe Something And We Don't Have the Words

### 2023-04-19 outputs/paper/paper.qmd
nitpicky

---
title: "We Are All Trying to Describe Something And We Don't Have the Words"
subtitle: "A Study of The Jack Antonoffification of Pop Music, and Propagating Uncertainty with Spotify"
author: 
  - Michaela Drouillard
thanks: "Code and data are available at: https://github.com/michaeladrouillard/jack."
date: today
abstract: "Using data from the Spotify API, I explored Jack Antonoff's production style and assessed whether Spotify's audio features can capture it. In an interview with Glen McDonald, an engineer at Spotify, I learned that the danceability and valence features were created by having interns tag songs as positive or gloomy, or danceable or un-danceable. Using a logistic regression model, I found that danceability was the most important feature in predicting Antonoff's involvement in a song. In the discussion section, I do a close-listen of Antonoff's most danceable songs, and argue that the danceability variable is actually capturing something more like a visceral quality to Antonoff's music."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "We Are All Trying to Describe Something And We Don't Have the Words"
subtitle: "A Study of The Jack Antonoffification of Pop Music (Or: Propagating Uncertainty with Spotify)"
author: 
  - Michaela Drouillard
thanks: "Code and data are available at: https://github.com/michaeladrouillard/jack."
date: today
abstract: "Using data from the Spotify API, I explored Jack Antonoff's production style and assessed whether Spotify's audio features can capture it. In an interview with Glen McDonald, an engineer at Spotify, I learned that the danceability and valence features were created by having interns tag songs as positive or gloomy, or danceable or un-danceable. Using a logistic regression model, I found that danceability was the most important feature in predicting Antonoff's involvement in a song. In the discussion section, I do a close-listen of Antonoff's most danceable songs, and argue that the danceability variable is actually capturing something more like a visceral quality to Antonoff's music."
format: pdf
number-sections: true
bibliography: references.bib
---
